The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
fst fig2 + quick cap

>>>>

<!-- TODO: work this cap -->
(ref:ml) Visualization of multilayer network for social ungulate case study. Six layers are presented with individuals shown as nodes, fixed in space across layers. Layer represent combinations of two seasons (winter and summer) and three landcover class (open, forest and forage). Edges connect individuals that associated according to spatial and temporal thresholds described above.

```{r ml, fig.cap='(ref:ml)'}
knitr::include_graphics('../graphics/figure-2.png')
```
